Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-04 paper/main.tex
Fix spaces
Minor intro reword

% no need to write the numbers in your introduction. You start by explaining what is happenning currently and then propose your solution.
The use of multiple antennas at the transmitter and receiver can significantly enhance the performance of wireless systems. Moreover, in these multiple-input multiple-output (MIMO) wireless systems, the transmitter can perform an better resource allocation if channel state information (CSI) is made available at the transmitter, both to improve data rates and reduce BER~\cite{love2008overview}. To this end, feeding back the channel state information from the receiver to the transmitter efficiently is necessary. In the many wireless systems that use orthogonal frequency division multiplexing (OFDM), the feedback needs to be provided to the transmitter across the many subcarriers of the system, which places a large feedback demand. However, since the channel state information varies gradually in both time and frequency, effective techniques to reduce feedback overheads exist, using frequency interpolation temporal prediction. In this paper, we focus on the problem of tracking the precoders of a MIMO-OFDM system across time and frequency for efficient CSI feedback.

In recent years, codebook design over the Stiefel Manifold \cite{6891198} has been proposed where the manifold structure of the channel matrix is used for its predictive quantization and interpolation across time and frequency. Another such variation of \cite{6891198} has exploited both time and frequency domain together in Stiefel Manifold \cite{Gupt1905:Predictive}. All these methods are useful, but they do so over Manifolds which has problems of getting stuck in local Maxima. Also, there are different challenged which are faced while interpolating in a high dimensional space.

Another very different approach in \cite{4114278} has tried to break down the precoder matrix into independent scalar parameters using transformations, namely Givens rotation and Household Transformation. They are tracking each of these scalar parameters using ADCPM(Adaptive Digital Pulse Code Modulation) for a slowly varying channel in the time domain. They have shown capacity achieved with the quantized precoding matrix to be very close to the unquantized one. In another paper \cite{4556174}, they have exploited frequency and performed ADPM in frequency domain to achieve similar performance with a lower number of feedback bits.

>>>>

% no need to write the numbers in your introduction. You start by explaining what is happenning currently and then propose your solution.
The use of multiple antennas at the transmitter and receiver can significantly enhance the performance of wireless systems. Moreover, in these multiple-input multiple-output (MIMO) wireless systems, the transmitter can perform an better resource allocation if channel state information (CSI) is made available at the transmitter, both to improve data rates and reduce BER~\cite{love2008overview}. To this end, feeding back the channel state information from the receiver to the transmitter efficiently is necessary. In the many wireless systems that use orthogonal frequency division multiplexing (OFDM), the feedback needs to be provided to the transmitter across the many subcarriers of the system, which places a large feedback demand. However, since the channel state information varies gradually in both time and frequency, effective techniques to reduce feedback overheads exist, using frequency interpolation temporal prediction. In particular, knowledge of the precoding matrices (that are typically the orthonormal right singular vectors of the channel matrix) is essential to enable the transmitter to transmite at capacity as well as to parallelize the channel. In this paper, we focus on the problem of tracking the precoders of a MIMO-OFDM system across time and frequency for efficient CSI feedback.

% TODO More coverage of prior work needed.
The problem of effective quantization and feedback of precoders for MIMO-OFDM attracted significant attention In recent years. Many approaches involve codebook design over the Stiefel Manifold~\cite{6891198}, wherein the manifold structure of the precoders is used to obtain tangents for predictive quantization and interpolation across time and frequency. Another such variation of \cite{6891198} has exploited both time and frequency domain together in Stiefel Manifold \cite{Gupt1905:Predictive}. All these methods are useful, but they do so over Manifolds which has problems of getting stuck in local Maxima. Also, there are different challenged which are faced while interpolating in a high dimensional space.

Other approaches have considered the problem of parametrizing precoding matrices using scalar parameters. It has been shown that the space of unitary matrices can be effectively parameterized using scalar parameters that correspond to Givens rotations and Household Transformations of the unitary precoding matrices~\cite{4114278,4556174}. By tracking these scalar parameters using adaptive digital pulse code modulation (ADPCM) for slowly varying channels in the time domain and the frequency domain, the link can operate close to capacity while using very few bits for quantization and feedback.
